Methods paper for erosion

### 2017-12-20 docs/methods/erosion_methods.tex
added figures
NM
Modified figures
Working on paper
Added area-drag figure
Writing a bit

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.9 \textwidth]{./figs/20bod.pdf}
\caption{20 bodies with vorticity}
\label{}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Figure generated using 20circ128.in with epsfac = 8, sigfac = 8, dt = 2e-4, fixpdrop = 1.
% Figure was made after the code changes regarding scaling the smoothing on the average stress on each body.

@@

For simplicity, we introduce the variables
\begin{align}
\label{eq:M}
& \Mterm = - 2 \pi \mean{\thalpha \Vn} \\
\label{eq:N}
& \NLterm = \frac{2 \pi}{L} \left( \pderiv{\atau}{\alpha} + \thalpha \Vs \right) \\
\label{eq:elfun}
& \elfun = \frac{2 \pi  \mean{\atau}}{L}
%\frac{4\pi^2}{L^{2} \log \left(2\pi/L \right)}
\end{align} 
Then Eq.~\eqref{eqn:thetaevo0} can be rewritten as
\begin{equation}
\label{eqn:thetaevo1}
\pderiv{\theta}{t} = \eps \elfun \ppd{\theta}{\alpha} + \NLterm
\end{equation}
Note that the highest-order, i.e.~stiff, term in Eq.~\eqref{eqn:thetaevo1} is {\em quasi-linear}. This is the key to the \thL method, and allows us to use very stable, implicit methods for this stiff term.

@@

%% TIME-STEPPING %%
\subsection{Time-stepping with the {\thL} method} 
We will evolve $\theta$ in spectral space, and so introduce the transforms
\todo[inline]{Check theta equation}
\begin{align}
& \theta(\alpha,t) = \alpha + \FourierSum \thhat_k e^{ i k \alpha} \\
& \NLterm(\alpha,t)  = \FourierSum \hat{\NLterm}_k e^{ i k \alpha}
\end{align}
Equation~\eqref{eqn:thetaevo1} gives a set of ODEs for the coefficients
\begin{equation}
\tderiv{\thhat_k}{t} +  \eps k^2  \elfun \thhat_k = \hat{\NLterm}_k
\end{equation}
We introduce the integrating factor
\begin{equation}
\label{eq:mu}
\mu_k = \exp \left( \eps k^2 \int \elfun \, dt \right)
\end{equation}
Then the evolution equations for $L$ and $\theta$ can be recast as the coupled system of ODEs
\begin{align}
\label{eqn:Levo2}
& \tderiv{L}{t} = \Mterm \\
\label{eqn:thetaevo2}
& \tderiv{}{t}\left( \mu_k \thhat_k \right) = \mu_k \hat{\NLterm}_k
\end{align}
We solve system \eqref{eqn:Levo2}--\eqref{eqn:thetaevo2} with an explicit, second-order Runge-Kutta method (RK2). In particular, we choose the {\em midpoint} RK2 method so as to maximize the smoothing effect of the curvature term.

@@

\subsection{Single-body validation results}

@@

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.99 \textwidth]{./figs/IntfacesStressArea.pdf}
\caption{One body}
\label{}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Figure from datafile 01circ1024aa;
% Uses 01circ1024.in with epsfac = 10, sigfac = 10, dt = 1e-6, fixpdrop = 0

@@

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.99 \textwidth]{./figs/fig4.pdf}
\caption{Final shape.}
\label{fig2}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%

>>>>

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.9 \textwidth]{./figs/50bod.pdf}
\caption{20 bodies with vorticity}
\label{}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Figure generated using 50circ128.in with epsfac = 10, sigfac = 10, dt = 2e-4, fixpdrop = 1.

@@

For simplicity, we introduce the variables
\begin{align}
\label{eq:M}
& \Mterm = - 2 \pi \mean{\thalpha \Vn} \\
\label{eq:N}
& \NLterm = \frac{2 \pi}{L} \left( \pderiv{\atau}{\alpha} + \thalpha \Vs \right) \\
\label{eq:elfun}
& \elfun = \frac{2 \pi  \mean{\atau}}{L}
%\frac{4\pi^2}{L^{2} \log \left(2\pi/L \right)}
\end{align} 
Then Eq.~\eqref{eqn:thetaevo0} can be rewritten as
\begin{equation}
\label{eqn:thetaevo1}
\pderiv{\theta}{t} = \eps \elfun \ppd{\theta}{\alpha} + \NLterm
\end{equation}
Note that the highest-order, i.e.~stiff, term in Eq.~\eqref{eqn:thetaevo1} is {\em quasi-linear}. This is the key to the {\thL} method, and allows us to use very stable, implicit methods for this stiff term.

@@

%% TIME-STEPPING %%
\subsection{Time-stepping with the {\thL} method} 
We will evolve $\theta$ in spectral space, and so introduce the transforms
\begin{align}
& \theta(\alpha,t) = \alpha + \FourierSum \thhat_k e^{ i k \alpha} \\
& \NLterm(\alpha,t)  = \FourierSum \hat{\NLterm}_k e^{ i k \alpha}
\end{align}
Recall that $\alpha = 2 \pi s / L$ is a normalized arc length.
Equation~\eqref{eqn:thetaevo1} gives a set of ODEs for the coefficients
\begin{equation}
\tderiv{\thhat_k}{t} +  \eps k^2  \elfun \thhat_k = \hat{\NLterm}_k
\end{equation}
We introduce the integrating factor
\begin{equation}
\label{eq:mu}
\mu_k = \exp \left( \eps k^2 \int \elfun \, dt \right)
\end{equation}
Then the evolution equations for $L$ and $\theta$ can be recast as the coupled system of ODEs
\begin{align}
\label{eqn:Levo2}
& \tderiv{L}{t} = \Mterm \\
\label{eqn:thetaevo2}
& \tderiv{}{t}\left( \mu_k \thhat_k \right) = \mu_k \hat{\NLterm}_k
\end{align}
We solve system \eqref{eqn:Levo2}--\eqref{eqn:thetaevo2} with an explicit, second-order Runge-Kutta method (RK2). In particular, we choose the {\em midpoint} RK2 method so as to maximize the smoothing effect of the curvature term.

@@

With the description of the numerical methods complete, we now present results on bodies eroding in Stokes flow. We first discuss simulations of a single eroding body, which can be compared with analytical results for validation, before discussing the erosion of many bodies.

\subsection{The erosion of a single body}

In the case of a single eroding body, certain analytical results can be derived regarding the limiting shape and vanishing rate. These results allow validation of our simulation.

@@

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.8 \textwidth]{./figs/shrink_intface.pdf}
\caption{One body}
\label{}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Figure from datafile 01circ1024aa;
% Uses 01circ1024.in with epsfac = 10, sigfac = 10, dt = 1e-6, fixarea = 0, fixpdrop = 0

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.8 \textwidth]{./figs/area_drag.pdf}
\caption{One body}
\label{}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Figure from datafile 01circ1024aa;
% Uses 01circ1024.in with epsfac = 10, sigfac = 10, dt = 1e-6, fixarea = 0, fixpdrop = 0

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.8 \textwidth]{./figs/fixed_intface.pdf}
\caption{One body fixed area}
\label{}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Figure from datafile 01circ1024c5
% Uses 01circ1024.in with epsfac = 5, sigfac = 5, dt = 2e-4, fixarea = 1, fixpdrop = 0

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.8 \textwidth]{./figs/arangle.pdf}
\caption{Aspect ration and opening angle}
\label{}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Figure from datafile 01circ1024c5
% Uses 01circ1024.in with epsfac = 5, sigfac = 5, dt = 2e-4, fixarea = 1, fixpdrop = 0

% Table
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{table}%[htbp]
\begin{center}
\caption{Final aspect ratio and opening angle
} 
\vspace{0.3 pc}
%\label{aaa}
\begin{tabular}{c c c}
\hline
\hspace{0.5pc} smoothing parameters, $\eps, \sigma$
\hspace{0.5pc} & final aspect ratio 
\hspace{0.5pc} & final opening angle \\
\hline
20/1024		& 2.55	& $110^\circ \pm 6^\circ$	\\
10/1024		& 2.62	& $104^\circ \pm 4^\circ$	\\
5/1024		& 2.65	& $102^\circ \pm 2^\circ$	\\
\hline
\end{tabular}
\end{center}
\end{table}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%

%\begin{comment}
% Table
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{table}%[htbp]
\begin{center}
\caption{Final aspect ratio and opening angle
} 
\vspace{0.3 pc}
%\label{aaa}
\begin{tabular}{l | c c c c}
\hline
{} & $\eps, \sigma = 20/1024$ & $\eps, \sigma = 10/1024$ & $\eps, \sigma = 5/1024$ & theoretical \\
\hline
final aspect ratio & 2.55 & 2.62 & 2.65 & -- \\
final opening angle & $110^\circ \pm 6^\circ$ & $104^\circ \pm 4^\circ$ & $102^\circ \pm 2^\circ$ & $102^\circ$
\end{tabular}
\end{center}
\end{table}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
%\end{comment}

@@
